A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-07-19 LensingPaper_draft_v4.02.tex
Included changes from Aaron.

%--------------------------------------------
\begin{abstract}
We investigate the matter distribution of a spiral galaxy with counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling. By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$. We model observed long-slit major axis stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations. The lens and dynamical model are independently derived, but in very good agreement with each other around $\sim R_\text{ein}$. We find that J1331's center requires a steep total mass-to-light ratio gradient. A dynamical model including a NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii. However, our models do not agree with the observed velocity dispersion at large radii. We speculate that the reason could be a non-trivial change in structure and kinematics due to a possible merger event in J1331's recent past.
\end{abstract}
%--------------------------------------------

@@

\NEW{The mass distribution of massive galaxies can be measured in completely independent fashions by gravitational lensing and dynamical modelling. Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content.}

Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images. This strong gravitational lensing tightly constrains the projected total mass of the lens galaxy inside $\sim 1''$ (e.g., \citealt{2010ARA&A..48...87T}).

The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile (e.g., \citealt{1980ApJ...238..471R}). However, due to its dissipative nature gas motions are very sensitive to disturbances by, e.g., spiral arms and bars (e.g., \citealt{2004dad..book.....S}).

Because stars are dissipationless dynamical tracers and present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii. As stellar motions are complex---a bulk rotation around one principal axis combined with random motions in all coordinate directions---\citep{2008gady.book.....B}, full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.

The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, which are (i) strong gravitational lenses and (ii) observed almost edge-on, such that rotation curves can be easily measured. By combining lensing and dynamical modelling, degeneracies inherent in both methods can be broken.

@@

%--------------------------------------------
J1331 is located at right ascension = 202.91800$^\circ$ and declination = 36.46999$^\circ$ (epoch J2000). \citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}. According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
%--------------------------------------------

@@

%--------------------------------------------
We use HST imaging of J1331 by \citet{SWELLSI}. They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip. The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$. In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness model of the reddish bulge.
%--------------------------------------------

@@

Inside of $\sim 4''$ the data appears to be symmetric; outside of it the data suggests that the assumption of axisymmetry seems not to be valid anymore. We subtract $2.3~\text{km s}^{-1}$ from $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity. We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} \geq 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data. In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 3.5''$ or $R' \lesssim 4''$ are used. Another reason to restrict the modelling to the bulge region is that our surface brightness model (Table \ref{tab:MGEF814W} and Figure \ref{fig:MGEinnerRegions}) is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
%--------------------------------------------

@@

%--------------------------------------------
$I(R',\theta')$ describes the intrinsic, to 2D projected light distribution or surface density of the galaxy. Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $i$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
\begin{equation}
\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right], \label{eq:deprojMGE}
\end{equation}
where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane. The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
\begin{eqnarray}
q_i^2 &=& \frac{q_i'^2 - \cos^2 i}{\sin^2 i}\\
\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
\end{eqnarray}
%--------------------------------------------

@@

%--------------------------------------------
A gravitational lens is a mass distribution whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens. We summarize the basic formalism (see also \citealt{1992grle.book.....S,1996astro.ph..6001N,2006glsw.conf....1S,2006glsw.conf...91K,2010ARA&A..48...87T}). The angular diameter distance from the observer to the lens is $D_d$, to the source plane $D_s$, and the distance between the lens and source plane is $D_{ds}$. The deflection potential of the lens is its potential projected along the line of sight $z'$ and rescaled to
\begin{equation}
\psi(\vect{\theta}) \OLD{:=}\NEW{\equiv} \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vect{r}=D_d \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
\end{equation}
where $\vect{\theta}\equiv(x',y')$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vect{\beta} \equiv (x_s',y_s')$ is deflected according to the lens equation
\begin{equation}
\vect{\beta} = \vect{\theta}_i - \left.\vect{\nabla}_\theta \psi(\vect{\theta})\right|_{\vect{\theta}_i} \label{eq:lenseqpot}
\end{equation}
into an image $\vect{\theta}_i = (x_i',y_i')$. The gradient of the deflection potential, $\vect{\nabla}_\theta \psi(\vect{\theta})$, is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.

\OLD{The total time delay of a deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
\begin{equation}
\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right]. \label{eq:timedelay}
\end{equation}
 According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.}

@@

The Einstein mass $M_\text{ein}$ and Einstein radius $R_\text{ein}$ are defined via the relation
\begin{equation}
M_\text{ein} \equiv M(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
\end{equation}
where 
\begin{equation}
\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}
\end{equation}
is the critical density and $M(<R_\text{ein})$ is the mass projected along the line-of-sight within $R'=R_\text{ein}$. $M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.
%--------------------------------------------

@@

\NEW{In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$). To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be}\OLD{$\langle v_i^2 \rangle$ is then} rotated by the inclination angle $i$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis. Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment \NEW{$\langle v_\text{los}^2\rangle(x',y')$}, which is comparable to actual spectroscopic measurements of the second velocity moment. Details of the derivation \NEW{of $\langle v_\text{los}^2\rangle(x',y')$ from the Jeans equations} using the MGE formalism are \OLD{given}\NEW{laid out} in \citet{Cap08} and in the appendix of \citet{GlennEC}. \OLD{We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,}\NEW{The result for $\langle v_\text{los}^2\rangle(x',y')$ in particular is given in Equation (28) and Equation (A18), respectively.}
\OLD{\begin{eqnarray}
&&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\nonumber\\
&&= 4 \pi^{3/2} G \int_0^1 \sum_{i=1}^N \sum_{k=1}^M \nu_{0,i} \ q_k \ \rho_{0,k} \ u^2\nonumber\\
&& \times \frac{\sigma_i^2 \ q^{2}_i \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,i}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_k) u^2 \right]}}\nonumber\\
&& \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \label{eq:explicitLOSvelCap}
\end{eqnarray}
with $N$ Gaussians describing the tracer distribution $\nu(R,z)$ and $M$ Gaussians describing the mass distribution $\rho(R,z)$, $\rho_{0,k}$ being the $k$-th mass density Gaussian evaluated at $(R=0,z=0)$ and
\begin{eqnarray*}
\mathscr{A} &=& \frac 12 \left(\frac{u^2}{\sigma_k^2} + \frac{1}{\sigma_i^2} \right)\nonumber\\
\mathscr{B} &=& \frac 12 \left\{\frac{1-q^{2}_i}{\sigma_i^2 q^{2}_i} + \frac{(1-q^{2}_k)u^4}{\sigma_k^2 \left[1-(1-{q}_k^{2})u^2 \right]} \right\}\nonumber\\
\mathscr{C} &=& 1- q^{2}_k - \frac{\sigma_i^2 q^{2}_i}{\sigma^2_k}\nonumber\\
\mathscr{D} &=& 1 - \frac{q^{2}_i}{1-\beta_{z,i}} - \left[ \left(1-\frac{1}{1-\beta_{i,z}}\right)\mathscr{C} + \frac{1-q^{2}_k}{1-\beta_{z,i}}\right] u^2.\nonumber
\end{eqnarray*}}

@@

%--------------------------------------------
As data we use stellar line-of-sight rotation velocities $v_\text{rot} = \langle v_\text{los} \rangle_\text{obs}$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data_kinematics}. The JAM models give a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle_\text{obs}$. The root-mean-square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to 
\begin{equation}
 v_\text{rms}^2 = v_\text{rot}^2 + \sigma^2  \stackrel{!}{=} \langle v_\text{los}^2 \rangle_\text{obs}.
\end{equation}
\OLD{The model in Equation \eqref{eq:explicitLOSvelCap}}\NEW{The model derived from the Jeans equations as outlined in Section \ref{sec:model_JAM_JAM}} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements. The measured $v_\text{rms}$ \NEW{in this work} is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
\begin{equation}
\text{AP}(x',y') \equiv \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' < + \frac{L_x}{2}\\
& \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
\end{equation}
The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV},
\begin{equation}
\text{PSF}(x',y')\equiv\mathscr{N}(0,\sigma_\text{seeing}=\text{FWHM}/2\sqrt{2\ln2}).
\end{equation}
The model predictions for $\langle v_\text{los}^2 \rangle_\text{intr}$ have therefore to be convolved with the convolution kernel
\begin{eqnarray}
K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \nonumber\\
&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
\end{eqnarray}
and weighted by the surface brightness $I(x',y')$, i.e.,
\begin{eqnarray}
I_\text{obs} &=& I \ast K\\
\langle v_\text{los}^2 \rangle_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle_\text{intr}) \ast K}{I_\text{obs}}.
\end{eqnarray}
\NEW{We modified the JAM code by \citet{Cap08} to use this convolution kernel with non-square pixels. The JAM code then}\OLD{If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap08}} performs the convolution numerically. We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
%--------------------------------------------

@@

%============================================
\begin{table}
\centering
\caption{General galaxy parameters of J1331.}
\begin{tabular}{lllr}
\hline
redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
angular diameter distance & $D_d$ [Mpc] & $414$ \\
scaling                   & $1~\text{kpc} / 1''$ & $2.006$ \\
position angle from North          & $\phi$ [$^\circ$] & $42.90$\\
average axis ratio & $q'$ & $0.598$\\
average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
estimated inclination & $i$ [$^\circ$] & $70$\\
apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
effective half-light radius & $R_\text{eff}$ [$''$] & $2.6$ \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table}
%============================================

>>>>

%--------------------------------------------
\begin{abstract}
We investigate the matter distribution of a spiral galaxy with \NEW{a} counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling. By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$. We model observed long-slit major axis stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations. The lens and dynamical model are independently derived, but in very good agreement with each other around $\sim R_\text{ein}$. We find that J1331's center requires a steep total mass-to-light ratio gradient. A dynamical model including a NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii. However, our models do not agree with the observed velocity dispersion at large radii. We speculate that the reason could be a non-trivial change in structure and kinematics due to a possible merger event in J1331's recent past.
\end{abstract}
%--------------------------------------------

@@

\NEW{The mass distribution of massive galaxies can be measured in completely independent fashions by gravitational lensing and dynamical modelling. Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content.} Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images. This strong gravitational lensing tightly constrains the projected total mass of the lens galaxy inside $\sim 1''$ (e.g., \citealt{2010ARA&A..48...87T}).

The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile (e.g., \citealt{1980ApJ...238..471R}). However, due to its dissipative nature gas motions are very sensitive to disturbances by, e.g., spiral arms and bars (e.g., \citealt{2004dad..book.....S}). Because stars are dissipationless dynamical tracers and present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii. As stellar motions are complex---a bulk rotation around one principal axis combined with random motions in all coordinate directions---\citep{2008gady.book.....B}, full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.

The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to \OLD{find}\NEW{finding} and \OLD{investigate}\NEW{investigating} spiral galaxies, which are (i) strong gravitational lenses and (ii) observed almost edge-on, such that rotation curves can be easily measured. By combining lensing and dynamical modelling, degeneracies inherent in both methods can be broken.

@@

%--------------------------------------------
J1331 is located at right ascension = 202.91800$^\circ$ and declination = 36.46999$^\circ$ (epoch J2000). \citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside \NEW{the projected radius on the sky} $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}. According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$. \NEW{We summarize all galaxy parameters also in Table \ref{tab:galaxyparameters}.}
%--------------------------------------------

@@

%--------------------------------------------
We use HST imaging of J1331 by \citet{SWELLSI}. They \OLD{performed}\NEW{obtained} high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip. The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$. In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness model of the reddish bulge.
%--------------------------------------------

@@

Inside of $\sim 4''$ the data appears to be symmetric; outside of it the data suggests that the assumption of axisymmetry seems not to be valid anymore. We subtract $2.3~\text{km s}^{-1}$ from $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity. We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} \OLD{\geq}\NEW{=} 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data. In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 3.5''$ or $R' \lesssim 4''$ are used. Another reason to restrict the modelling to the bulge region is that our surface brightness model (Table \ref{tab:MGEF814W} and Figure \ref{fig:MGEinnerRegions}) is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
%--------------------------------------------

@@

%--------------------------------------------
$I(R',\theta')$ describes the intrinsic\OLD{, to} \NEW{and} 2D projected light distribution or surface density of the galaxy. Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $\OLD{i}\NEW{inc}$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
\begin{equation}
\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right], \label{eq:deprojMGE}
\end{equation}
where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.\footnote{\NEW{$(R,z)$ are cylindrical coordinates aligned with the galactic plane. The primed $(R',z')$ denote polar coordinates on the plane of the sky.}} The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
\begin{eqnarray}
q_i^2 &=& \frac{q_i'^2 - \cos^2 \OLD{i}\NEW{(inc)}}{\sin^2 \OLD{i}\NEW{(inc)}}\\
\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
\end{eqnarray}
%--------------------------------------------

@@

%--------------------------------------------
A gravitational lens is a mass distribution whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens. We summarize the basic formalism (see also \citealt{1992grle.book.....S,1996astro.ph..6001N,2006glsw.conf....1S,2006glsw.conf...91K,2010ARA&A..48...87T}). The angular diameter distance from the observer to the lens is $D_\text{d}$, to the source plane $D_\text{s}$, and the distance between the lens and source plane is $D_\text{ds}$. The deflection potential of the lens is its potential projected along the line of sight $z'$ and rescaled to
\begin{equation}
\psi(\vect{\theta}) \OLD{:=}\NEW{\equiv} \frac{D_\text{ds}}{D_\text{d} D_\text{s}} \frac{2}{c^2} \int \Phi(\vect{r}=D_\text{d} \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
\end{equation}
where $\vect{\theta}\equiv(x',y')$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vect{\beta} \equiv (x_s',y_s')$ is deflected according to the lens equation
\begin{equation}
\vect{\beta} = \vect{\theta}_i - \left.\vect{\nabla}_\theta \psi(\vect{\theta})\right|_{\vect{\theta}_i} \label{eq:lenseqpot}
\end{equation}
into an image $\vect{\theta}_i = (x_i',y_i')$. The gradient of the deflection potential, $\vect{\nabla}_\theta \psi(\vect{\theta})$, is equal to the angle by which the light is deflected multiplied by $D_\text{ds}/D_\text{s}$.

\OLD{The total time delay of a deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
\begin{equation}
\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_\text{d} D_\text{s}}{D_\text{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right]. \label{eq:timedelay}
\end{equation}
 According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.}

@@

The Einstein mass $M_\text{ein}$ and Einstein radius $R_\text{ein}$ are defined via the relation
\begin{equation}
M_\text{ein} \equiv M(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
\end{equation}
where 
\begin{equation}
\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_\text{s}}{D_\text{d} D_\text{ds}}
\end{equation}
is the critical density and $M(<R_\text{ein})$ is the mass projected along the line-of-sight within $R'=R_\text{ein}$. $M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.
%--------------------------------------------

@@

\NEW{In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$). To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be}\OLD{$\langle v_i^2 \rangle$ is then} rotated by the inclination angle $\OLD{i}\NEW{inc}$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis. Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment \NEW{$\langle v_\text{los}^2\rangle(x',y')$}, which is comparable to actual spectroscopic measurements of the second velocity moment. Details of the derivation \NEW{of $\langle v_\text{los}^2\rangle(x',y')$ from the Jeans equations} using the MGE formalism are \OLD{given}\NEW{laid out} in \citet{Cap08} and in the appendix of \citet{GlennEC}. \OLD{We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,}\NEW{The result for $\langle v_\text{los}^2\rangle(x',y')$ in particular is given in Equation (28) and Equation (A18), respectively.}
\OLD{\begin{eqnarray}
&&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\nonumber\\
&&= 4 \pi^{3/2} G \int_0^1 \sum_{i=1}^N \sum_{k=1}^M \nu_{0,i} \ q_k \ \rho_{0,k} \ u^2\nonumber\\
&& \times \frac{\sigma_i^2 \ q^{2}_i \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,i}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_k) u^2 \right]}}\nonumber\\
&& \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \label{eq:explicitLOSvelCap}
\end{eqnarray}
with $N$ Gaussians describing the tracer distribution $\nu(R,z)$ and $M$ Gaussians describing the mass distribution $\rho(R,z)$, $\rho_{0,k}$ being the $k$-th mass density Gaussian evaluated at $(R=0,z=0)$ and
\begin{eqnarray*}
\mathscr{A} &=& \frac 12 \left(\frac{u^2}{\sigma_k^2} + \frac{1}{\sigma_i^2} \right)\nonumber\\
\mathscr{B} &=& \frac 12 \left\{\frac{1-q^{2}_i}{\sigma_i^2 q^{2}_i} + \frac{(1-q^{2}_k)u^4}{\sigma_k^2 \left[1-(1-{q}_k^{2})u^2 \right]} \right\}\nonumber\\
\mathscr{C} &=& 1- q^{2}_k - \frac{\sigma_i^2 q^{2}_i}{\sigma^2_k}\nonumber\\
\mathscr{D} &=& 1 - \frac{q^{2}_i}{1-\beta_{z,i}} - \left[ \left(1-\frac{1}{1-\beta_{i,z}}\right)\mathscr{C} + \frac{1-q^{2}_k}{1-\beta_{z,i}}\right] u^2.\nonumber
\end{eqnarray*}}

@@

%--------------------------------------------
As data we use stellar line-of-sight rotation velocities $v_\text{rot} = \langle v_\text{los} \rangle_\text{obs}$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data_kinematics}. The JAM models give a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle_\text{obs}$. The root-mean-square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to 
\begin{equation}
 v_\text{rms}^2 = v_\text{rot}^2 + \sigma^2  \stackrel{!}{=} \langle v_\text{los}^2 \rangle_\text{obs}.
\end{equation}
\OLD{The model in Equation \eqref{eq:explicitLOSvelCap}}\NEW{The model derived from the Jeans equations as outlined in Section \ref{sec:model_JAM_JAM}} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements. The measured $v_\text{rms}$ \NEW{in this work} is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
\begin{equation}
\text{AP}(x',y') \equiv \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' < + \frac{L_x}{2}\\
& \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
\end{equation}
The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV},
\begin{equation}
\text{PSF}(x',y')\equiv\mathscr{N}(0,\sigma_\text{seeing}=\text{FWHM}/2\sqrt{2\ln2}).
\end{equation}
The model predictions for $\langle v_\text{los}^2 \rangle_\text{intr}$ have therefore to be convolved with the convolution kernel
\begin{eqnarray}
K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \nonumber\\
&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[\text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) \right.\nonumber\\
 && + \left. \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
 \end{eqnarray}
and weighted by the surface brightness $I(x',y')$, i.e.,
\begin{eqnarray}
I_\text{obs} &=& I \ast K\\
\langle v_\text{los}^2 \rangle_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle_\text{intr}) \ast K}{I_\text{obs}}.
\end{eqnarray}
\NEW{We modified the JAM code by \citet{Cap08} to use this convolution kernel with non-square pixels. The JAM code then}\OLD{If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap08}} performs the convolution numerically. We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
%--------------------------------------------

@@

%============================================
\begin{table}
\centering
\caption{General galaxy parameters of J1331.}
\begin{tabular}{lllr}
\hline
redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
angular diameter distance & $D_\text{d}$ [Mpc] & $414$ \\
scaling                   & $1~\text{kpc} / 1''$ & $2.006$ \\
position angle from North          & $\phi$ [$^\circ$] & $42.90$\\
average axis ratio & $q'$ & $0.598$\\
average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
estimated inclination & $\OLD{i}\NEW{inc}$ [$^\circ$] & $70$\\
apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
effective half-light radius & $R_\text{eff}$ [$''$] & $2.6$ \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table}
%============================================
